\chapter{Project presentation}


\section{Presentation of the subject}

The subject of this project revolves around the creation of a sophisticated system dedicated to predicting sports outcomes. The main objective is to develop a robust tool capable of providing accurate predictions for various sports competitions. This system aims to leverage statistical data to generate victory probabilities, offering an insightful perspective on the expected performances of teams.

\section{Project aims}

\textbf{Overall Objective}\\
The fundamental objective of this project is the design and implementation of an advanced sports outcome prediction system. Efforts are concentrated on achieving two main goals:\\
\begin{quote}
\textbf{1) Modeling Victory Probabilities}\\
The first major objective is to develop a program capable, when presented with two teams (A and B), of generating a probability (p) representing the chance of victory for team A. This also involves determining the complementary probability of victory for team B (1−p).\\

\\
\textbf{2) Prediction of Finalists and Championship Results}\\
In a broader perspective, the project aims to process data from a specific championship to identify the finalist teams and predict the probability of victory for each finalist in the decisive match.\\
\end{quote}
\\
\textbf{Methodological Approach}\\
To achieve these objectives, the methodological approach proposes the implementation of two distinct regressors. The first one uses a random forest (RF) model, while the second relies on a neural network (NN) with a multi-layer perceptron model.\\
\\
\textbf{Parameter Optimization}\\
Emphasis is placed on the pursuit of excellence through the determination of an optimal set of parameters for each regressor. This critical step aims to ensure maximum performance when predicting probabilities.\\
\\
\textbf{Model Evaluation and Selection}\\
The last step of the methodological approach involves evaluating the performance of the models. Tools such as the confusion matrix and various performance indicators derived from it will be used to choose the model that offers the most reliable and accurate results. In summary, the project combines an advanced algorithmic approach with methodological rigor to provide probable and informative sports predictions. These predictions apply to both specific match-ups and larger-scale competitions.
